\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-14 doc/sui14/iteration1.tex

As for the qualitative feedback, 11 out of \changes{16} participants preferred IR selection over list mode (\changes{3} preferred list, \changes{2} was undecided). \changes{When asked: \studyquote{When you have multiple candidate targets within sight, which method for selecting between did you use?} (multiple choices), among 16 participates, 81\% chose {\em adjust head so that only one candidate is signaled}, 56\% chose {\em tap (to enter refinement stage) and then choose between list}, and 25\% chose {\em walk closer to the candidate for a better result}. Although through our observation, many participants walked one or two steps during some tasks, this suggests that participants viewed their moving as a followed-through action of adjusting their heads instead of an intention to walk closer to the targets.

>>>>

As for the qualitative feedback, 11 out of \changes{16} participants preferred IR selection over list mode (\changes{3} preferred list, \changes{2} was undecided). \changes{When asked: \studyquote{When you have multiple candidate targets within sight, which method for selecting between them did you use?} (multiple choices), among 16 participates, 81\% chose {\em adjust head so that only one candidate is signaled}, 56\% chose {\em tap (to enter refinement stage) and then choose between list}, and 25\% chose {\em walk closer to the candidate for a better result}. Although through our observation, many participants walked one or two steps during some tasks, this suggests that participants viewed their moving as a followed-through action of adjusting their heads instead of an intention to walk closer to the targets.

### 2014-08-14 doc/sui14/iteration2.tex

We have empirically measured the intensity distribution at the receiver for this configuration in Figure~\ref{fig:measurement}. Our measurements confirm that angular difference has a large effect on the intensity readings (see how the IR intensity distribution changes when the \changes{angle has increased}).

@@

\sean{If possible, add how we observed participants physical movements in this iteration. Better if we can compare to i1.} One side effect that we have observed in this approach is that the {\em Intensity IR} sometimes eliminates the desired target during the {\em scanning} stage. Out of 300 trials, \changes{the target is accidentally eliminated in 13 (4.3\%).} This is higher than the error rate for {\em Naive IR} (5 out of 300, ~1.6\%). \changes{Even though the higher error rate increases the chance of multiple attempts in target selection, our analysis above illustrates that overall performance of {\em Intensity IR} is still better than {\em Naive IR}. }  % but this is the trade-off for the overall faster acquisition time.

>>>>

We have empirically measured the intensity distribution at the receiver for this configuration in Figure~\ref{fig:measurement}. Our measurements confirm that angular difference has a large effect on the intensity readings (see how the IR intensity distribution changes when the \changes{angle has increased}) \achal{this sounds awkward to me - maybe "Note the changes in IR intensity distribution when the angle increases}.

@@

\sean{If possible, add how we observed participants physical movements in this iteration. Better if we can compare to i1.} One side effect that we have observed in this approach is that the {\em Intensity IR} sometimes eliminates the desired target during the {\em scanning} stage. Out of 300 trials, \changes{the target was accidentally eliminated in 13 (4.3\%).} This is higher than the error rate for {\em Naive IR} (5 out of 300, ~1.6\%). \changes{Even though the higher error rate increases the chance of multiple attempts in target selection, our analysis above illustrates that overall performance of {\em Intensity IR} is still better than {\em Naive IR}. }  % but this is the trade-off for the overall faster acquisition time.
